Universal Anonymous Signatures

### 2022-06-17 prism-backend/research/gsac/app-model-related.tex
Added model and proofs for Revocable ACs.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

\paragraph{Security of \CUASAC.} %
We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }
      \vspace*{0.75em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
          \Verify(\cdot,\cdot)\rangle$} \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,n]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,Obtiss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
    of the issuer with public key \ipk. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
    be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
  where $\ipk^{n-1}$ is the public key of the parent issuer,
  $\fissue^{n,\dattrs}$ is an issuance function as described in
  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
  delegate..
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
  credentials.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
  required by the issuer.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
\end{description}

@@

\iffalse
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

  \begin{description}
  \item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs a variant of \IKeyGen from
  our \CUASGen construction where, instead of using a conventional signature
  scheme, the issuer leverages its own anonymous credential of level $n$ to
  create a signature in which it only reveals the credential level. That is,
  $\sig_{is} \gets \CUASGen.Sign(\isk,\opk',\cred,\msg_{is},\feval^{0,n})$,
  for some random $\msg_{is}$, and $\opk'$ from \parm, where $\feval^{0,n}$ is a
  signing evaluation function that reveals no attribute other than the level
  of the credential. Let $\opk_{n-1}$ be the issuer of the credential \cred
  (i.e., an issuer with level $n-1$). The current issuer of level $n$ publishes
  its public key as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] As in \CUASAC.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  As in \CUASAC.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  As in \CUASAC, but using $\feval^{\dattrs,n}$ as signature evaluation
  function.
\end{description}

\paragraph{Security of \CUASDAC.} %
We need to define $level(\opk,n)$. This function first parses \parm
as $(\parm',\opk')$, and \opk as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$,
and returns $\CUASGen.Verify(\opk_{n-1},\opk',\sig_{is},n,\msg_{is},
\feval^{0,n})$.

Given $level$, the security proofs are as for \CUASAC, with the addition that,
in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
can be directly used to break the sign unforgeability property of the underlying
\CUASGen scheme.
\fi

>>>>

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

\paragraph{Security of \CUASAC.} %
We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pccomment{Abort if challenge creds belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }
      \vspace*{0.5em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pccomment{Abort if challenge sigs belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        \langle\cdot,(b,\utrans)\rangle \gets
        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,n]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
    of the issuer with public key \ipk. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

@@

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
    be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
  where $\ipk^{n-1}$ is the public key of the parent issuer,
  $\fissue^{n,\dattrs}$ is an issuance function as described in
  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
  delegate..
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
  credentials.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
  required by the issuer.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
\end{description}

@@

\subsection{Revocable Anonymous Credentials}
\label{sapp:related-models-rac}

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, all credentials get an identifier as first attribute,
and \feval functions prove that the opener can retrieve that identifier. Then,
in case of needing to revoke a concrete credential, any verifier can interact
with the opener to add an identifier to its own revocation list (alternatively,
there can be a public list of revoked credentials). Having \feval functions
prove that the credential identifier does not belong to that list thus directly
implements privacy-preserving revocation. We first give a simple model in
\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
before, for simplicity we assume only one credential is used per authentication
(the extension being direct). To the functionality in
\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
(equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
credential used in a presentation transcript \utrans -- and which is essentially
equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
verifiable openings, but this would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %

For our RAC construction, we define signature evaluation and opening functions
as follows:

\begin{align}
  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
    \lbrace
    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
    \pcelse \pcreturn (\dattrs(\cred),V)
    \rbrace \nonumber \\
  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
    \lbrace
    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
    \pcelse \pcreturn 0
     \rbrace
  \label{eq:funcs-rac}
\end{align}

Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way function $F$
(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
selectively disclosed by signers, a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by this verifier. If the credential used for
signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
an indication that the signature should be rejected by the verifier. Otherwise,
it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
$\yeval^1$ will be encrypted with a single-use key pair.
%
On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
valid signatures to be locally revocable by $V$ at a later stage, since
$\yeval^1=V$.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  \CUASGen construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Outputs the revocation handle $h$ for the credential used in the interactive
  presentation associated to \utrans. Note that $h$ is verifier-dependent.
\end{description}

\paragraph{Security of \CUASRAC.} %
We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
  anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
  \CUASGen as defined in \defref{def:sign-anonymity-uas}.

  First observe that, given a revocation handle $F(V,id)$ extracted from any
  credential showing, it is not possible to extract $id$, as $F$ is one-way.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
  open transcripts from challenge users (signatures, in the non-interactive
  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
  so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~ against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against sign
  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game via the winning condition of line 6 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~ winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.  
  %
  \qed
\end{proof}
